% --- LaTeX CV Template - S. Venkatraman ---

% --- Set document class and font size ---

\documentclass[letterpaper, 11pt]{article}

% --- Package imports ---

\usepackage{hyperref, enumitem, longtable, amsmath, array}
\usepackage{alltt}
% --- Page layout settings ---

% Set page margins
\usepackage[left=0in, right=0.1in, bottom=0.6in, top=0.6in, headsep=0in, footskip=0.2in]{geometry}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{tabto}
\newcommand\mytab{\tabto{0.5cm}}

% Set line spacing

\renewcommand{\baselinestretch}{1}

% --- Page formatting settings ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=MidnightBlue, urlcolor=MidnightBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage{CJKutf8}
% Remove page numbering
\pagenumbering{arabic}%or arabic

% Define font size and color for section headings, use MidnightBlue for default
\newcommand{\headingfont}{\Large\color{black}}

% --- CV section settings ---

% Note: each section of this table (Education, Awards, Publications etc.) is
% stored in a two-column table. The left-hand column is narrow (1 inch) and is
% meant to store dates. The right-hand column is wide (5.2 inches) and stores
% the main text.  Sections in which each entry might have multiple lines
% (e.g., Education) are stored in a 'SectionTable' environment). Sections in
% which each entry might just have one line are stored in a 'SectionTableSingleSpace'
% environment. The only difference between the two environments is the line
% spacing between each entry. Both environments take one argument, which is the
% title of the section. See main document for how these environments are used.

% Define settings for left-hand column in which dates are printed

\newcolumntype{R}{>{\raggedright \scriptsize}p{0.45in}}

% Define 'SectionTable' environment
\newenvironment{SectionTable}[1]{
	\renewcommand*{\arraystretch}{1.5}
	\setlength{\tabcolsep}{10pt}
	\begin{longtable}{Rp{6.3in}} & #1 \vspace{0.13cm}\hrule\\}
{\end{longtable}\vspace{-.3cm}}

% Define 'SectionTableSingleSpace' environment
\newenvironment{SectionTableSingleSpace}[1]{
	\renewcommand*{\arraystretch}{1.3}
	\setlength{\tabcolsep}{10pt}
	\begin{longtable}{Rp{6.3in}} & #1 \vspace{0.13cm}\hrule \\[0.6em] }
{\end{longtable}\vspace{-.3cm}}

% Define tile table environment
\newenvironment{TitleTable}[1]{
	\renewcommand*{\arraystretch}{1.6}
	\setlength{\tabcolsep}{10pt}
	\begin{longtable}{Rp{6.3in}} & #1\\}
{\end{longtable}\vspace{-.3cm}}

% --- Document starts here ---

\begin{document}
% --- Name and contact information ---

\begin{TitleTable}
	{\huge{{Baichen Du}} \hspace{1cm}\Large{[pai3 ʈʂʰən2 tʷu:4]}} &
Department of Linguistics, \hfill Email: \href{mailto::baichen@connect.hku.hk}{baichen@connect.hku.hk}\newline
The University of Hong Kong \hfill URL: \href{https://baichen-du.github.io}{https://baichen-du.github.io}\newline
Run Run Shaw Tower, Pokfulam Road, HK\\
%Github: \href{https://github.com/baichen-du}{baichen-du} \& \href{https://github.com/albertbaichendu}{albertbaichendu}\\
\end{TitleTable}
% --- Section: Research interests ---

\begin{SectionTable}{\headingfont{\textbf{\textsc{Research Interests}}}}
{\scriptsize{Topics}} & \textbf{Phonetics \& Phonology:} Experimental and developmental phonology and phonetics, acoustic, auditory, and articulatory phonetics, speech perception, sound change, multiple cues \\
%\footnotesize Methodology & Computer vision as articulometry in audiovisual phonetics research: Emotion and facial expression detection and tracking, facial landmarks tracking.\\
\end{SectionTable}

% --- Section: Education ---

\begin{SectionTableSingleSpace}{\headingfont{\textbf{\textsc{Education}}}}

\raggedright{\scriptsize{2025-}} &
\textbf{University of California, Los Angeles}\newline \textsc{Ph.D in Linguistics} \vspace{0.3cm}\\

\raggedright{\scriptsize{2025-}} &
\textbf{University of California, Los Angeles}\newline \textsc{M.A in Linguistics} \vspace{0.3cm}\\

\raggedright{\scriptsize{2019-2024}} &
\textbf{The University of Hong Kong}\newline
\textsc{Bachelor of Social Sciences} with the Highest Honor Distinction (\textit{summa cum laude})\newline
\textit{Majors:} Politics and Public Administration; Linguistics\newline
\textit{Advisors:} Jonathan Havenhill, Haohan Chen \vspace{0.3cm}\\

&
{\normalfont{\textsc{Non-degree trainings}}}\\

\raggedright{\scriptsize{2023}} &
\textbf{University of California, Berkeley}, Undergraduate Visiting Student \\
2021 &
\textbf{The Luso-Brazillian Association of Linguistics}\\

\raggedright{\scriptsize{2020-2022}}&
\textbf{Korea University,} {Int'l Summer \& Winter Campus}\\
%& \textbf{Selected coursework}
%\begin{itemize}[itemsep=0pt, leftmargin=*]
%\item \textit{Statistics}: Asymptotic statistics, Mathematical statistics, Functional data analysis, High-dimensional statistics, Information theory
%\item \textit{Mathematics}: Measure theory, Functional analysis, Measure-theoretic probability with martingales
%\end{itemize}

\end{SectionTableSingleSpace}

% --- Section: Publications ---
\begin{SectionTableSingleSpace}{\headingfont{\textbf{\textsc{Publications \& Manuscripts}}}}
&\textsc{Invited articles}\\
\raggedright{\scriptsize{2024}}&
\textbf{Du, B.}, Pfiffner, A., Johnson, K. \normalfont{Visible articulatory variation as a cue to sound change: Lip rounding and lip protrusion variability in the Mandarin sibilant merger.} \textit{{University of Pennsylvania Working Papers in Linguistics, 30}}(2). \\

&\textsc{Contributed articles}\\
\raggedright{\scriptsize{In prep}}&
\textbf{Du, B.,} Alexandra A. \normalfont{Multiple and cross-modality cue integration and weighting: Lip rounding and acoustic cues in the Mandarin sibilant merger}\\

\raggedright{\scriptsize{To appear}}&
\textbf{Du, B.} \normalfont{Acoustic distance effect on the perception of sibilants mergers between retroflexes and alveolars in Taiwan Mandarin. In} \textit{\normalfont{\textit{Proceedings of Seventh Annual Berkeley Undergraduate Linguistics Symposium 2023}}. Linguistic Society of University of California, Berkeley, CA} \\

\raggedright{\scriptsize{Accepted}} &
 \normalfont{Do, Y.\textsuperscript{*}}, \normalfont{Van Hoey, T., Yu, X.,} \textbf{Du, B.}, \normalfont{Tan, L. } {Implicit and explicit learning of vowel harmony patterns in phonotactics and alternations}\\


% \centerline{In prep} &
%   \textbf{Du, B.} \normalfont{ An audio-visual account for synchronic sound changes towards sibilants merger in Taiwan Mandarin. In} \textit{\normalfont{\textit{Proceedings of Meetings on Acoustics 184ASA}}. Acoustical Society of America, 2023} \\
%   \newpage
\raggedright{\scriptsize{2023}} &
\textbf{Du, B.} \normalfont{\textit{The backfire effect in the perception and judgement of congruent and incongruent interpretation of political propaganda.} Undergraduate Thesis of Political Psychology, University of Hong Kong, HK.} \\
\newpage

 %  &
%  \normalfont{Soderstrom, M.\textsuperscript{*}, Casar, M.}, \textbf{Du, B.} (In prep). Examining infant language experiences in a cross-cultural context \\

\end{SectionTableSingleSpace}

\begin{SectionTableSingleSpace}{\headingfont{\textbf{\textsc{Presentations}}}}
&
{\textit{(As presenting author)}}\\
&
\textsc{\normalsize{{Workshops}}}\\
\raggedright{\scriptsize{2023}} &
\textbf{Du, B.} \normalfont{(2023, Sep). {Introduction to Advanced R Programming with RMarkdown.} The Sociolinguistic Lab at UC Berkeley.}\\
&
\textsc{{Conference Papers and Posters}}\\

\raggedright{\scriptsize{2023}} &
\textbf{Du, B.}\normalfont{, Pfiffner, A., Johnson, K. (2024, Jan). The role of visible articulatory variation in the Mandarin sibilant contrast and merger.} Paper presented at the 98th Annual Meeting of Linguistic Society of America (LSA2024), New York City, NY. \\
%\newpage
%\pagenumbering{arabic}


\raggedright{\scriptsize{2023}} &
\normalfont{Havenhill, J, \textbf{Du, B}. (2023, Dec). The role of visual cues in sound change: A cross-modality perceptual account for the typological rarity of labial palatalization.} Poster to be presented at the 185th Meeting of Acoustical Society of America (ASA185), Sydney, Australia.\\

\raggedright{\scriptsize{2023}} &
 \textbf{Du, B.}, \normalfont{Pfiffner, A., Johnson, K. (2023, Dec). Consonant and vowel rounding: same acoustics, different visuals.} Poster to be presented at the 185th Meeting of Acoustical Society of America (ASA185), Sydney, Australia.\\


 \raggedright{\scriptsize{2023}}&
\textbf{Du, B.}\normalfont{, Pfiffner, A., Johnson, K. (2023, Oct). Visible articulatory variation as a cue to sound change: Lip rounding and lip protrusion variability in the Mandarin sibilant merger. Paper presented at {New Ways of Analyzing Variation 51 (NWAV51), Queens College CUNY, New York City, NY.}} \href{https://docs.google.com/presentation/d/15aB5uoF73BXkLEtXdfhLGwyTWoB4F2DoGlLK8vTo9DY/edit?usp=sharing}{Slides}.\\

\raggedright{\scriptsize{2023}}&
\textbf{Du, B.} \normalfont{(2023, May). Acoustic distance effect on the perception of sibilants mergers between retroflexes and alveolars in Taiwan Mandarin.} Poster presented at the {184th Meeting of Acoustical Society of America 2023 (ASA 184), Chicago, IL.} DOI: \href{https://doi.org/10.1121/10.0019189}{10.1121/10.0019189}. \\

\raggedright{\scriptsize{2023}} &
\textbf{Du, B.} \normalfont{(2023, Apr). An audio-visual account for synchronic sound changes towards sibilants merger in Taiwan Mandarin.} Talk given at the {Seventh Annual Berkeley Undergraduate Linguistics Symposium 2023, University of California, Berkeley, CA.} \\

\raggedright{\scriptsize{2023}} &
\textbf{Du, B.} \normalfont{(2023, Apr). The backfire effect in the perception and judgement of congruent and incongruent interpretation of political propaganda.} Poster presented at {Undergraduate Research Fellowship Program Poster Session: Student Research Posters, University of Hong Kong, HK.} \\

\end{SectionTableSingleSpace}

% \begin{SectionTable}{\headingfont{\textbf{Work-in-progress}}}
% \raggedright{\scriptsize{In progress}}&
%   \normalfont{\textbf{Du, Baichen}, Pfiffner, Alexandra, Johnson, Keith. Adaptive  cue weightings in production and perception of palatal contrast in Korean} \\

%  &
%  \normalfont{Havenhill, Jonathan\textsuperscript{*}}, \textbf{Du, Baichen}. Cross-modal cue integration and phonological evolution: An audio-visual account for palatalization and sound change in diachronic and synchronic Time \\

%  &
%  \normalfont{Pfiffner, Alexandra\textsuperscript{*}}, \textbf{ Du, Baichen.} The acoustics of plosive lenition in Dutch \\

% %  &
% %  \normalfont{Do, Youngah\textsuperscript{*}}, Sze, Sui Lung,\textbf{ Du, Baichen}, Ho, To Tsz, Li, Tak Wang. Bilingual speakers’ performance in simultaneous generalization of multiple phonological patterns \\
% \end{SectionTable}


% --- Section: Teaching experience ---

% \begin{SectionTable}{\headingfont Teaching experience}
% Fall 2020 &
% \textbf{Teaching assistant, STAT 123: Course name here (University)} \newline
% Topics and description of your responsibilities. Aliquam volutpat est vel massa. Sed dolor lacus, imperdiet non, ornare non, commodo eu, neque. \newline
% \textit{Average student rating: X/5.} \\

% Spring 2020 &
% \textbf{Teaching assistant, MATH 234: Course name here (University)} \newline
% Topics and description of your responsibilities. Aliquam volutpat est vel massa. Sed dolor lacus, imperdiet non, ornare non, commodo eu, neque. \newline
% \textit{Average student rating: X/5.}
% \end{SectionTable}

% --- Section: Industry experience ---

% \begin{SectionTable}{\headingfont Industry experience}
% Summer 2020 &
% \textbf{Name of company (Title of job or internship)} -- City, State \newline
% Description of your responsibilities. Integer pretium semper justo. Proin risus. Nullam id quam. Nam neque. Phasellus at purus et lib ero lacinia dictum.  \\

% Summer 2019 &
% \textbf{Name of company (Title of job or internship)} -- City, State \newline
% Description of your responsibilities. Integer pretium semper justo. Proin risus. Nullam id quam. Nam neque. Phasellus at purus et lib ero lacinia dictum.  \\

% Summer 2018 &
% \textbf{Name of company (Title of job or internship)} -- City, State \newline
% Description of your responsibilities. Integer pretium semper justo. Proin risus. Nullam id quam. Nam neque. Phasellus at purus et lib ero lacinia dictum.  \\
% \end{SectionTable}

% --- Section: Talks and tutorials ---
\begin{SectionTable}{\headingfont{\textbf{\textsc{Grants and Fundings}}}}

2023 &
Down Funder Student Travel Funding, ASA: \hfill US\$1,000\newline\textit{185th Meeting of Acoustical Society of America \& 2023 Meeting of the Australian Acoustical Society, Syndey}\\

2023 &
UC Berkeley Departmental Instruction Grants:\hfill US\$600 \newline\textit{Audiovisual production of Mandarin sibilants \& Cross-modal cue integration and weighting in the perception of Mandarin high front vowel contrast}  \\

2022&
HKU Transdisciplinary Undergraduate Research Initiative Grant: \hfill HK\$3,830\newline\textit{An audio-visual account for linguistic and social selectivity in the accommodation to sibilant mergers in Mandarin}  \\

2022&
HKU Leung Kau Kui Research and Teaching Endowment:\hfill US\$1,300\newline \textit{The backfire effect in the perception and judgement of congruent and incongruent interpretation of political propaganda} \\
\end{SectionTable}\newpage

\begin{SectionTableSingleSpace}{\headingfont{\textbf{\textsc{Honors and Awards}}}}
2023&
Ms Cecilia Vong Prize of Linguistics  \hfill HK\$1,000\\
2022&
Globalink Research Award, Mitacs \hfill CA\$12,000 \\
2022&
Undergraduate Research Fellowship \hfill HK\$10,000\\
2022&
K.K.Ho Prize  \hfill US\$2,560 \\
2022&
Dean's Honor List\hfill \\
2021&
Dean's Honor List\hfill \\
2020&
Dean's Honor List\hfill \\
2019&
Soong Ching-ling Foundation Scholarship  \hfill US\$ 30,700 \\
\end{SectionTableSingleSpace}



% --- Section: Research experience ---

\begin{SectionTable}{\headingfont{\textbf{\textsc{Research Experience}}}}


&\textsc{Undergraduate Experience}\\
	%&
	%\normalsize \textbf{UC Berkeley}\\
 2023 &
 \textbf{Korean tonogenesis among native and heritage speakers} \hfill{UC Berkeley}\newline
 \textbf{Multiple adaptive cue weighting in Korean palatal contrast}\newline
 \textbf{Mandarin sibilant merger and differential cue weightings}\newline
	\textit{PI:} Dr. Keith Johnson\newline
	\textit{Roles:} Independent projects on cue weightings and bilingualism, study design, experimentation, analyses and manuscript preparation.
	\\
2023 &
	\textbf{Integration of emotion in speech perception}\hfill Polytechnic University of Hong Kong\newline 
	\textit{PIs:} Dr. Keith Johnson, Dr. Yao Yao\newline
	\textit{Roles:} Leading project on smiling speech. Study design, experiment programing, administering audiovidual production, facial expression tracking and action unit analysis, audiovisual alignment and segmentation.\\
	%Assistance to study design, experimental programming, participant recuriting, emotion and facial expression detection and tracking using CNN, eye tracking and behavioral data collection. \\
	%&
	%\normalsize \textbf{Univ. of HK}\\
2023 &
\textbf{Audiovisual perception of Korean labial palatalization} \hfill University of Hong Kong \newline
	\textit{PIs:} Dr. Jonathan Havenhill\newline
	\textit{Roles:} Acoustic analysis, speech manipulation and synthesis with KlattGrid, audiovisual stimuli creation, experiment programming, analyses and presentation\\

2022 &
\textbf{The ManyBaby project} \hfill University of Manitoba \newline \textit{PI:} Prof. Melaine Soderstrom. \newline
\textit{Roles:} Acoustic measurement, statistical modelling of prosodic changes in Child Directed Speech\\
	%Assistance to automatic pitch measurement using Praat, performing statistical analysis in R. \\

2022 &
\textbf{The backfire effect in the perception of political views} \hfill University of Hong Kong \newline 
\textit{Advisor:} Dr. Haohan Chen\newline
\textit{Roles:} Conducting this independent study, including web data extraction using R, analyzing and interpreting text data. Compiling tutorials of advanced data science course of POLI3148: Data Science in Politics and Public Administration.\\

2021-22&
\textbf{Learnability of vowel rounding harmony for kids and adults} \hfill University of Hong Kong \newline 
\textit{PI:} Dr. Youngah Do \newline
\textit{Roles:} Study design, stimuli creation, experiment programming, data analysis, manuscript preparation \\

	% &
	%Independent study titled "The backfire effect in the perception and judgement of congruent and incongruent interpretation of political propaganda". Assisting web data extraction using R. Analyzing and interpreting text data. Compiling tutorials of advanced data science course for POLI3148: Data Science in Politics and Public Administration. \\

	%&
	%\normalsize \textbf{Univ. of Manitoba}\\
	\end{SectionTable}

% --- Section: Mentorship and service ---
%\newpage
\begin{SectionTable}{\headingfont{\textbf{\textsc{Skills}}}}
Language &
English, Mandarin, Cantonese\\

Scripting &
R, Praat Scripting, \LaTeX, Markdown, HTML, Python\\

Tools &
\textbf{Statistics:} RStudio, jamovi\newline
\textbf{Experiment:} PsychoPy, EyeLink 1000 Plus, Pavlovia.org\newline
\textbf{Measurement:} Praat, OpenFace, Qualtrics\newline
\textbf{Processing:} Klatt Synthesis, Montreal Forced Alignment, TANDAM-STRAIGHT, ffmpeg, ELAN, Polly\newline
\textbf{Recruitment:} Mechanical Turk, Prolific\\

Others &
\textbf{Statistical Modelling:}{ Frequentist and Bayesian statistics (e.g., Linear/Generalized Mixed Effects Regression)}, Structural Equation Modeling (e.g., EFA, CFA, Latent Growth Model, Multi-level Modelling), \newline
\textbf{Text Data Processing:} web data extraction, topic modelling, sentiment analysis\newline
\textbf{Computer Vision:} Facial Landmarks Tracking, Emotion Detection, Eye Tracking\\
\end{SectionTable}

% --- Section: Mentorship and service ---

\begin{SectionTableSingleSpace}{\headingfont{\textbf{\textsc{Memberships and Services}}}}
2023-&
Acoustical Society of America \hfill Student member\\
2021-&
Linguistic Society of America \hfill Student member\\

2023 &
Mitacs \hfill Globalink Research Ambassador \\
2022&
 Undergraduate Buddy Program \hfill Mentor to Fu Jia'ni \\
2021-23&
Chinese Culture Committee at R.C.Lee Hall \hfill Chariperson\\
2020-21&
Social Service Fund, HKUSU \hfill External Secretary\\
2021&
Pad for Hope Foundation \hfill Teaching Assistant\\
2020&
University Service Centre of CUHK \hfill Student Helper\\
\end{SectionTableSingleSpace}

% --- Section: Professional society memberships ---
%\newpage
% \begin{SectionTableSingleSpace}{\headingfont Relevant Coursework}
% Linguistics &
% Phonetics (A), Advanced Phonetics (A), Experimental Phonetics (A+), Phonology (A+), \newline Phonetic-Phonology interface (A+), Variation analysis (A-), Advanced Sociolinguistics (A), \newline Laboratory linguistics (A),  Second language research (A+), Languages of the world (A+), \newline Grammatical description (A+), Semantics (A-), Language Revitalization (Pending).\\

% Methods &
% Advanced Statistics in Psychology (Pending), Research Methods in Social Sciences (A+), \newline Data Science in Politics and Public Administration (A+), Policy and Program Evaluation (A-),\newline Data Analysis with R (A)\\
% \end{SectionTableSingleSpace}

% \begin{SectionTableSingleSpace}{\headingfont{References}}
% 	&
% 		\textbf{Dr. Alexandra Pfiffner}\newline
% 		Lecturer at UC Berkeley\newline
% 		\href{https://www.alexandra-pfiffner.com/}{alexandra-pfiffner.com}\newline
% 		apfiffner@berkeley.edu\newline

% 		\textbf{Prof. Keith Johnson}\newline
% 		Professor of Graudate School at UC Berkeley\newline
% 		\href{https://linguistics.berkeley.edu/~kjohnson/}{linguistics.berkeley.edu/~kjohnson}\newline
% 		keithjohnson@berkeley.edu\newline

% 		\textbf{Dr. Jonathan Havenhill}\newline
% 		Assistant Professor at Univ. of HK\newline
% 		\href{https://jhavenhill.com}{jhavenhill.com}\newline
% 		jhavenhill@hku.hk
% \end{SectionTableSingleSpace}
%  \begin{SectionTable}{\headingfont References}
%  &
%  \textbf{Dr. Alexandra Pfiffner}\newline
%  Lecturer at UC Berkeley\newline
%  \href{https://www.alexandra-pfiffner.com/}{alexandra-pfiffner.com}\newline
%  apfiffner@berkeley.edu\\
%  &
%  \textbf{Prof. Keith Johnson}\newline
%  Professor of Graudate School at UC Berkeley\newline
%  \href{https://linguistics.berkeley.edu/~kjohnson/}{linguistics.berkeley.edu/~kjohnson}\newline
%  keithjohnson@berkeley.edu\\
%  &
%  \textbf{Dr. Jonathan Havenhil}\newline
%  Assistant Professor at Univ. of HK\newline
%  \href{https://jhavenhill.com}{jhavenhill.com}\newline
%  jhavenhill@hku.hk\\
%  &
%  \textbf{Dr. Youngah Do}\newline
%  Associate Professor at Univ. of HK\newline
%  \href{https://repository.hku.hk/cris/rp/rp02160}{repository.hku.hk/cris/rp/rp02160}\newline
%  youngah@hku.hk\\
%  &
%  \textbf{Dr. Haohan Chen}\newline
%  Assistant Professor at Univ. of HK\newline
%  \href{https://haohanchen.github.io}{haohanchen.github.io}\newline
%  haohan@hku.hk\\

%  \end{SectionTable}

\mbox{}
%\vfill
%\begin{center}
%Last update: \today
%\end{center}
% --- End of CV! ---

\end{document}





