% --- LaTeX CV Template - S. Venkatraman ---

% --- Set document class and font size ---

\documentclass[letterpaper, 11pt]{article}

% --- Package imports ---

\usepackage{hyperref, enumitem, longtable, amsmath, array}

% --- Page layout settings ---

% Set page margins
\usepackage[left=0in, right=0.1in, bottom=0.5in, top=0.5in, headsep=0in, footskip=0.2in]{geometry}
\usepackage{multicol}
\usepackage{hyperref}
% Set line spacing
\renewcommand{\baselinestretch}{1}

% --- Page formatting settings ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=MidnightBlue, urlcolor=MidnightBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage{CJKutf8}
% Remove page numbering
\pagenumbering{gobble}%or arabic

% Define font size and color for section headings
\newcommand{\headingfont}{\Large\color{MidnightBlue}}

% --- CV section settings ---

% Note: each section of this table (Education, Awards, Publications etc.) is
% stored in a two-column table. The left-hand column is narrow (1 inch) and is
% meant to store dates. The right-hand column is wide (5.2 inches) and stores
% the main text.  Sections in which each entry might have multiple lines
% (e.g., Education) are stored in a 'SectionTable' environment). Sections in
% which each entry might just have one line are stored in a 'SectionTableSingleSpace'
% environment. The only difference between the two environments is the line
% spacing between each entry. Both environments take one argument, which is the
% title of the section. See main document for how these environments are used.

% Define settings for left-hand column in which dates are printed
\newcolumntype{R}{>{\raggedleft}p{0.6in}}

% Define 'SectionTable' environment
\newenvironment{SectionTable}[1]{
	\renewcommand*{\arraystretch}{1.7}
	\setlength{\tabcolsep}{10pt}
	\begin{longtable}{Rp{6.3in}} & #1 \\}
{\end{longtable}\vspace{-.3cm}}

% Define 'SectionTableSingleSpace' environment
\newenvironment{SectionTableSingleSpace}[1]{
	\renewcommand*{\arraystretch}{1.2}
	\setlength{\tabcolsep}{10pt}
	\begin{longtable}{Rp{6.3in}} & #1 \\[0.6em]}
{\end{longtable}\vspace{-.3cm}}

% --- Document starts here ---

\begin{document}

% --- Name and contact information ---

\begin{SectionTable}{\huge Baichen Du} &
Oct, 2023 \newline
Email: \href{mailto::baichen@connect.hku.hk}{baichen@connect.hku.hk} \& \href{mailto::albertbaichendu@berkeley.edu}{albertbaichendu@berkeley.edu}\newline
Webpage: \href{https://baichen-du.github.io}{baichen-du.github.io}\newline
Twitter: \href{https://twitter.com/_15abcd}{\_15abcd}\newline
%Github: \href{https://github.com/baichen-du}{baichen-du} \& \href{https://github.com/albertbaichendu}{albertbaichendu}\\
\end{SectionTable}
% --- Section: Research interests ---

\begin{SectionTable}{\headingfont Research Interests}
Topics & Phonetics \& Phonology: experimental phonology and phonetics, acoustic, auditory, and articulatory phonetics, speech production and perception, developmental phonetics and phonology, sound change, cue integration, weighting, and trading. \\
%\footnotesize Methodology & Computer vision as articulometry in audiovisual phonetics research: Emotion and facial expression detection and tracking, facial landmarks tracking.\\
\end{SectionTable}

% --- Section: Education ---

\begin{SectionTable}{\headingfont Education}
2023 -- 2024 &
\textbf{University of California, Berkeley} \newline
- Undergraduate Visiting Student of Linguistics \newline
- Advisor: Dr. Alexandra Pfiffner. \newline - GPA: 4.0 out of 4.0. \\

2019 -- 2024 &
\textbf{University of Hong Kong} \newline
- B.Soc.Sc, Politics and Public Administration \& Linguistics \newline
- Advisors: Dr. Jonathan Havenhill, Dr. Youngah Do, Dr. Haohan Chen. \newline - GPA: 3.93 out of 4.3, GPA of Linguistics: 4.12 (Top 1). \\
%& \textbf{Selected coursework}
%\begin{itemize}[itemsep=0pt, leftmargin=*]
%\item \textit{Statistics}: Asymptotic statistics, Mathematical statistics, Functional data analysis, High-dimensional statistics, Information theory
%\item \textit{Mathematics}: Measure theory, Functional analysis, Measure-theoretic probability with martingales
%\end{itemize}

\end{SectionTable}

% --- Section: Publications ---


\begin{SectionTable}{\headingfont Publications \& Manuscripts}
To appear&
\textbf{Du, Baichen.} \normalfont{Acoustic distance effect on the perception of sibilants mergers between retroflexes and alveolars in Taiwan Mandarin. In} \textit{\normalfont{\textit{Proceedings of Seventh Annual Berkeley Undergraduate Linguistics Symposium 2023}}. Linguistic Society of University of California, Berkeley, CA} \\

Revising &
 \normalfont{Do, Youngah\textsuperscript{*}}, \normalfont{Van Hoey, Thomas, Yu, Xiaoyu,} \textbf{Du, Baichen}, \normalfont{Tan, Lihui. } {Implicit and explicit learning of vowel harmony patterns in phonotactics and alternations}\\

In Prep &
 \textbf{Du, B.} \normalfont{ An audio-visual account for synchronic sound changes towards sibilants merger in Taiwan Mandarin. In} \textit{\normalfont{\textit{Proceedings of Meetings on Acoustics 184ASA}}. Acoustical Society of America, 2023} \\


2023 &
\textbf{Du, Baichen} \normalfont{\textit{The backfire effect in the perception and judgement of congruent and incongruent interpretation of political propaganda.} Undergraduate Thesis of Political Psychology, University of Hong Kong, HK.} \\

 %  &
%  \normalfont{Soderstrom, M.\textsuperscript{*}, Casar, M.}, \textbf{Du, B.} (In prep). Examining infant language experiences in a cross-cultural context \\

\end{SectionTable}

\begin{SectionTable}{\headingfont Presentations}
&
\textbf{\normalsize{\textit{Workshops}}}\\
2023 &
\textbf{Du, Baichen} \normalfont{(2023, Sep). {Introduction to Advanced R Programming with RMarkdown.} The Sociolinguistic Lab at University of California, Berkeley.} \href{https://baichen-du.github.io/assets/SocioSkillShareSep12/SocioSkillShare_Sep12_BD.html#/title-slide}{Slides}.\\
\newpage
&
\textbf{\textit{Conference Papers and Posters}}\\

2023 &
\textbf{Du, Baichen}\normalfont{, Pfiffner, Alexandra, Johnson, Keith. (2024, Jan). The role of visible articulatory variation in the Mandarin sibilant contrast and merger.} Talk to be given at the 98th Annual Meeting of Linguistic Society of America (LSA2024), New York City, NY. \\

2023 &
\normalfont{Havenhill, Jonathan, \textbf{Du, Baichen}. (2023, Dec). The role of visual cues in sound change: A cross-modality perceptual account for the typological rarity of labial palatalization.} Poster to be presented at the 185th Meeting of Acoustical Society of America \& 2023 Meeting of the Australian Acoustical Society (ASA185), Sydney, Australia.\\

2023 &
 \textbf{Du, Baichen}, \normalfont{Pfiffner, Alexandra, Johnson, Keith. (2023, Dec). Consonant and vowel rounding: same acoustics, different visuals.} Poster to be presented at the 185th Meeting of Acoustical Society of America \& 2023 Meeting of the Australian Acoustical Society (ASA185), Sydney, Australia.\\


2023&
\textbf{Du, Baichen}\normalfont{, Pfiffner, Alexandra, Johnson, Keith. (2023, Oct). Visible articulatory variation as a cue to sound change: Lip rounding and lip protrusion variability in the Mandarin sibilant merger. Talk to be given at {New Ways of Analyzing Variation: Variation in World's Languages (NWAV51), Queens College CUNY, New York City, NY.}}\\

2023 &
\textbf{Du, Baichen.} \normalfont{(2023, May). Acoustic distance effect on the perception of sibilants mergers between retroflexes and alveolars in Taiwan Mandarin.} Poster presented at the {184th Meeting of Acoustical Society of America 2023 (ASA 184), Chicago, IL.} DOI: \href{https://doi.org/10.1121/10.0019189}{10.1121/10.0019189}. \\

2023 &
\textbf{Du, Baichen.} \normalfont{(2023, Apr). An audio-visual account for synchronic sound changes towards sibilants merger in Taiwan Mandarin.} Talk given at the {Seventh Annual Berkeley Undergraduate Linguistics Symposium 2023, University of California, Berkeley, CA.} \\

2023 &
\textbf{Du, Baichen.} \normalfont{(2023, Apr). The backfire effect in the perception and judgement of congruent and incongruent interpretation of political propaganda.} Poster presented at {Undergraduate Research Fellowship Program Poster Session: Student Research Posters, University of Hong Kong, HK.} \\

\end{SectionTable}

\begin{SectionTable}{\headingfont Work-in-progress}
 In Prep &
  \normalfont{\textbf{Du, Baichen}, Pfiffner, Alexandra, Johnson, Keith. Adaptive  cue weightings in production and perception of palatal contrast in Korean} \\
&
 \normalfont{Yao, Yao\textsuperscript{*}}, \textbf{Du, Baichen}, \& Johnson, Keith. Production and perception of smiling speech: Implications for sound change.\\

 &
 \normalfont{Havenhill, Jonathan\textsuperscript{*}}, \textbf{Du, Baichen}. Cross-modal cue integration and phonological evolution: An audio-visual account for palatalization and sound change in diachronic and synchronic Time \\

 &
 \normalfont{Pfiffner, Alexandra\textsuperscript{*}}, \textbf{ Du, Baichen.} The acoustics of plosive lenition in Dutch \\

 &
 \normalfont{Do, Youngah\textsuperscript{*}}, Sze, Sui Lung,\textbf{ Du, Baichen}, Ho, To Tsz, Li, Tak Wang. Bilingual speakers’ performance in simultaneous generalization of multiple phonological patterns \\
\end{SectionTable}


% --- Section: Teaching experience ---

% \begin{SectionTable}{\headingfont Teaching experience}
% Fall 2020 &
% \textbf{Teaching assistant, STAT 123: Course name here (University)} \newline
% Topics and description of your responsibilities. Aliquam volutpat est vel massa. Sed dolor lacus, imperdiet non, ornare non, commodo eu, neque. \newline
% \textit{Average student rating: X/5.} \\

% Spring 2020 &
% \textbf{Teaching assistant, MATH 234: Course name here (University)} \newline
% Topics and description of your responsibilities. Aliquam volutpat est vel massa. Sed dolor lacus, imperdiet non, ornare non, commodo eu, neque. \newline
% \textit{Average student rating: X/5.}
% \end{SectionTable}

% --- Section: Industry experience ---

% \begin{SectionTable}{\headingfont Industry experience}
% Summer 2020 &
% \textbf{Name of company (Title of job or internship)} -- City, State \newline
% Description of your responsibilities. Integer pretium semper justo. Proin risus. Nullam id quam. Nam neque. Phasellus at purus et lib ero lacinia dictum.  \\

% Summer 2019 &
% \textbf{Name of company (Title of job or internship)} -- City, State \newline
% Description of your responsibilities. Integer pretium semper justo. Proin risus. Nullam id quam. Nam neque. Phasellus at purus et lib ero lacinia dictum.  \\

% Summer 2018 &
% \textbf{Name of company (Title of job or internship)} -- City, State \newline
% Description of your responsibilities. Integer pretium semper justo. Proin risus. Nullam id quam. Nam neque. Phasellus at purus et lib ero lacinia dictum.  \\
% \end{SectionTable}

% --- Section: Talks and tutorials ---

\begin{SectionTable}{\headingfont Grants and Fundings}

2023 &
Down Funder Student Travel Funding, Acoustical Society of America: \textit{185th Meeting of Acoustical Society of America \& 2023 Meeting of the Australian Acoustical Society, Syndey} \hfill US\$1,000\\

2023 &
UC Berkeley Departmental Instruction Grants: \textit{Audiovisual production of Mandarin sibilants \& Cross-modal cue integration and weighting in the perception of Mandarin high front vowel contrast} \hfill US\$600 \\

2022&
HKU Transdisciplinary Undergraduate Research Initiative Grant: \textit{An audio-visual account for linguistic and social selectivity in the accommodation to sibilant mergers in Mandarin} \hfill HK\$3,830 \\

2022&
HKU Leung Kau Kui Research and Teaching Endowment: \textit{The backfire effect in the perception and judgement of congruent and incongruent interpretation of political propaganda.}\hfill US\$1,300 \\
\end{SectionTable}

\begin{SectionTableSingleSpace}{\headingfont Honors and Awards}
2023&
Ms Cecilia Prize of Linguistics  \hfill HK\$1,000\\
2022&
Globalink Research Award, Mitacs \hfill CA\$12,000 \\
2022&
K.K.Ho Prize  \hfill US\$2,560 \\
2022&
Dean's Honor List\hfill \\
2021&
Dean's Honor List\hfill \\
2020&
Dean's Honor List\hfill \\
2019&
Soong Ching-ling Foundation Scholarship  \hfill US\$ 30,700 \\
\end{SectionTableSingleSpace}



% --- Section: Research experience ---

\begin{SectionTableSingleSpace}{\headingfont Research Experience}

	%&
	%\normalsize \textbf{UC Berkeley}\\
 2023 &
	Undergraduate Research Apprenticeship Program \hfill Dr. Alexandra Pfiffner \\
	2023&
	Supervised Independent Study \hfill Dr. Alexandra Pfiffner\\
	%Assistance to TextGrid segmentation and auto-alignment of boundaries by Praat scripting. \\

	%&
	%\normalsize \textbf{Polytechnic Univ. of HK}\\
2023 &
	Speech and Language Science Lab, Hong Kong Polytechnic University \hfill Dr. Yao Yao \\
	%Assistance to study design, experimental programming, participant recuriting, emotion and facial expression detection and tracking using CNN, eye tracking and behavioral data collection. \\
	%&
	%\normalsize \textbf{Univ. of HK}\\
2023 &
	Student Research Assistant \hfill Dr. Jonathan Havenhill \\

	% &
	%Assistance to Study design, audiovisual stimuli creation, experimental programming in PsychoPy and Pavolovia.org using Python and Javascript, subjects recuriting, data collection, statistical modelling (e.g., Genearlized Linear Mixed-effects Models) using R, Manuscripts preparation.\\

2022 &
	Undergraduate Research Fellowship Program \hfill Dr. Haohan Chen \\
	2022&
	Student Research Assistant \hfill Dr. Haohan Chen \\

	2021-22&
	Language Development Lab \hfill Dr. Youngah Do \\


2021 &
	Undergraduate Research Opportunity Program \hfill Dr. Jonathan Havenhill\\

	% &
	%Independent study titled "The backfire effect in the perception and judgement of congruent and incongruent interpretation of political propaganda". Assisting web data extraction using R. Analyzing and interpreting text data. Compiling tutorials of advanced data science course for POLI3148: Data Science in Politics and Public Administration. \\

	%&
	%\normalsize \textbf{Univ. of Manitoba}\\
2022 &
	The Baby Language Lab, University of Manitoba-Winnipeg \hfill Prof. Melaine Soderstrom. \\
	%Assistance to automatic pitch measurement using Praat, performing statistical analysis in R. \\

	\end{SectionTableSingleSpace}

% --- Section: Mentorship and service ---
%\newpage
\begin{SectionTableSingleSpace}{\headingfont Skills}
Languages &
English, Mandarin, Cantonese\\

\small Programming &
R, Praat Scripting, \LaTeX, Markdown, HTML, Python\\

Research Tools &
\textbf{Statistics:} RStudio, jamovi\newline
\textbf{Experiment:} PsychoPy, EyeLink 1000 Plus, Pavlovia.org\newline
\textbf{Measurement:} Praat, OpenFace, Qualtrics\newline
\textbf{Processing:} Klatt Synthesis, Montreal Forced Alignment, TANDAM-STRAIGHT, ffmpeg, ELAN, Polly\newline
\textbf{Recruitment:} Mechanical Turk, Prolific\\

Research Skills &
\textbf{Statistical Modelling:}{ Frequentist and Bayesian statistics (e.g., Linear/Generalized Mixed Effects Regression)}, Structural Equation Modeling (e.g., EFA, CFA, Latent Growth Model, Multi-level Modelling), \newline
\textbf{Text Data Processing:} web data extraction, topic modelling, sentiment analysis\newline
\textbf{Computer Vision:} Facial Landmarks Tracking, Emotion Detection, Eye Tracking\\
\end{SectionTableSingleSpace}

% --- Section: Mentorship and service ---

\begin{SectionTableSingleSpace}{\headingfont Membership and Service}
2023-&
Acoustical Society of America \hfill Student member\\
2021-&
Linguistic Society of America \hfill Student member\\

2023 &
Mitacs \hfill Globalink Research Ambassador \\
2022&
 Undergraduate Buddy Program \hfill Mentor to Fu Jia'ni \\
2021-23&
Chinese Culture Committee at R.C.Lee Hall \hfill Chariperson\\
2020-21&
Social Service Fund, HKUSU \hfill External Secretary\\
2021&
Pad for Hope Foundation \hfill Teaching Assistant\\
2020&
University Service Centre of CUHK \hfill Student Helper\\
\end{SectionTableSingleSpace}

% --- Section: Professional society memberships ---
%\newpage
\begin{SectionTableSingleSpace}{\headingfont Relevant Coursework}
Linguistics &
Phonetics (A), Advanced Phonetics (A), Experimental Phonetics (A+), Phonology (A+), \newline Phonetic-Phonology interface (A+), Variation analysis (A-), Advanced Sociolinguistics (A), \newline Laboratory linguistics (A),  Second language research (A+), Languages of the world (A+), \newline Grammatical description (A+), Semantics (A-), Language Revitalization (Pending).\\

Methods &
Advanced Statistics in Psychology (Pending), Research Methods in Social Sciences (A+), \newline Data Science in Politics and Public Administration (A+), Policy and Program Evaluation (A-),\newline Data Analysis with R (A)\\
\end{SectionTableSingleSpace}\vspace{-1.5cm}

%\begin{SectionTable}{}
%	& \begin{multicols*}{2}
%		{\headingfont References}\vspace{0.5cm}\newline
%		\textbf{Dr. Alexandra Pfiffner}\newline
%		Lecturer at UC Berkeley\newline
%		\href{https://www.alexandra-pfiffner.com/}{alexandra-pfiffner.com}\newline
%		apfiffner@berkeley.edu\newline
%
%		\textbf{Prof. Keith Johnson}\newline
%		Professor of Graudate School at UC Berkeley\newline
%		\href{https://linguistics.berkeley.edu/~kjohnson/}{linguistics.berkeley.edu/~kjohnson}\newline
%		keithjohnson@berkeley.edu\newline
%
%		\textbf{Dr. Jonathan Havenhil}\newline
%		Assistant Professor at Univ. of HK\newline
%		\href{https://jhavenhill.com}{jhavenhill.com}\newline
%		jhavenhill@hku.hk\columnbreak\newline
%
%		\vspace{0.5cm}\textbf{Dr. Youngah Do}\newline
%		Associate Professor at Univ. of HK\newline
%		\href{https://repository.hku.hk/cris/rp/rp02160}{repository.hku.hk/cris/rp/rp02160}\newline
%		youngah@hku.hk\newline
%
%		\textbf{Dr. Haohan Chen}\newline
%		Assistant Professor at Univ. of HK\newline
%		\href{https://haohanchen.github.io}{haohanchen.github.io}\newline
%		haohan@hku.hk\newline
%	\end{multicols*}
%\end{SectionTable}
% \begin{SectionTable}{\headingfont References}
% &
% \textbf{Dr. Alexandra Pfiffner}\newline
% Lecturer at UC Berkeley\newline
% \href{https://www.alexandra-pfiffner.com/}{alexandra-pfiffner.com}\newline
% apfiffner@berkeley.edu\\

% &
% \textbf{Prof. Keith Johnson}\newline
% Professor of Graudate School at UC Berkeley\newline
% \href{https://linguistics.berkeley.edu/~kjohnson/}{linguistics.berkeley.edu/~kjohnson}\newline
% keithjohnson@berkeley.edu\\

% &
% \textbf{Dr. Jonathan Havenhil}\newline
% Assistant Professor at Univ. of HK\newline
% \href{https://jhavenhill.com}{jhavenhill.com}\newline
% jhavenhill@hku.hk\\

% &
% \textbf{Dr. Youngah Do}\newline
% Associate Professor at Univ. of HK\newline
% \href{https://repository.hku.hk/cris/rp/rp02160}{repository.hku.hk/cris/rp/rp02160}\newline
% youngah@hku.hk\\

% &
% \textbf{Dr. Haohan Chen}\newline
% Assistant Professor at Univ. of HK\newline
% \href{https://haohanchen.github.io}{haohanchen.github.io}\newline
% haohan@hku.hk\\

% \end{SectionTable}

\mbox{}
%\vfill
%\begin{center}
%Last update: \today
%\end{center}
% --- End of CV! ---

\end{document}





